\begin{otherlanguage}{ngerman}
\begin{abstract}
  Hier werden auf einer halben bis ganzen Seite die Kernaussagen der Arbeit
  auf Deutsch zusammengefasst.
  \bigskip\par
  \textbf{Stichw"orter:} HPC, OpenMP
\end{abstract}
\end{otherlanguage}
\begin{otherlanguage}{english}
\begin{abstract}
  In 2014, the Neurorobotics team of the Blue Brain Project (BBP), project of the Ecole Federale Polytechnique
Federale de Lausanne (EPFL), successfully produced a point-neuron model of a mouse brain from data
provided by the Allen Institute for Brain Science (Provide reference of Allen Institute). Using NEST software, the
BBP Neurorobotics team was then able to simulate a scaled-down model of the mouse brain on a laptop
computer, paving the way towards making a mouse brain interact with an environment. A full-scale
implementation of the mouse brain model is possible, but requires the of large scale resources with low latency
requirements only modern supercomputers can today provide.The current functionality of NEST supports
generating large neuronal networks on a super computer based an random distributions but not yet from
experimental data contained in brain atlases. We suggest as part of this thesis to first develop the means to fully
model a mouse brain from experimental data using NEST software on available supercomputing architectures.
Building from this experience, we wish to work on accelerating NEST computation up to real time so that the
study of mouse brain plasticity becomes tractable. Leveraging from this new set of functionalities, we plan to
derive network requirements for the HBP to drive the design of the HBP network across supercomputing centers
so that both neurorobotics and interactive supercomputing applications can be demonstrated.

The neuronal spiking network simulator NEST is developed in C++ and delivers an user interface based on an
own description language SLI and and a Python interface. The new use case shall be integrated into the
standard work flow of NEST. Besides the functionality in C++ the interfaces have to be extended. The difficulties
of the network generation is based on a difference in the NEST internal data structure and the data delivered by
the Allen Institute. Connection information contains target and source neurons besides biochemical information
of the synapses. Because of the in vitro injection methods the connection information maps the synapse from
the source to the target neurons. For multi process simulations NEST distributes all neurons based on a modulo
function to the processes. Because of memory optimizations the synapses are only stored on the post synaptic
process. This means that the connection information is stored
on the process, where the target neuron is located. Therefore a transformation of the given data is necessary.
Preprocessing of the input data should be avoided as far as possible to capture future use cases. The resulting
implementation shall load the connection information efficiently in parallel, distribute the synapse information to
the post synaptic node and store it in the NEST data structure. Further requirements of the implementation are
an efficient use of the available resources as memory and computation power.
  \bigskip\par
  \textbf{Keywords:} HPC, OpenMP
\end{abstract}
\end{otherlanguage}
